---
title: "EDA - P3"
author: "Charlie Heller and Jyoti Tyagi"
date: "November 25, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Final Project, P3 - Exploratory Data Analysis


#### Finsish tidying data
Per instructor feedback (pasted below) there are a few tweaks left that we need to make in order to tidy our data. We'll address these points first, then conduct our EDA

Good start, but you missed a couple important points: 

1) Your data is not yet tidy. Tidy means one observation per row, not one subject with a number of similar observations. As the data is currently formatted, it will be impossible for you to use the tidy or infer pipelines to explore or analyze your data. You'll need to "gather" the many columns into something approximately like:

        subject_id, pre_or_post, decorated_or_sparse, lesson, [distraction_type], result

Note: It's reasonable to leave the test scores and time-off-task in two tables, since the time-off-task has many subtypes. However, you may need to merge them (after tidying and summarizing) for some of your analyses.

2) In addition, you should be using the raw data, dropping any summary columns or tables and re-creating them (if needed) using the raw data and R. This would also result in a much shorter code book.

##### Tidy the data
We'll start by loading the data. We'll use the same function (defined below) from our last submission to read this back in.

* First, load libraries
```{r echo=TRUE, eval=TRUE}
library(readxl)
library(tidyverse)
```

* define loading function
```{r echo=TRUE, eval=TRUE}
read_excel_allsheets <- function(filename, tibble = TRUE) {
    sheets <- readxl::excel_sheets(filename)
    x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X, skip=2))
    if(!tibble) x <- lapply(x, as.data.frame)
    names(x) <- sheets
    x
}
```

* load the data
```{r echo=TRUE, eval=TRUE}
data_tables <- read_excel_allsheets(here::here("Data", "vis_att_data.xlsx"))
```

* okay, now we've loaded the data into a list of dataframes. The first dataframe is the codebook, and the second is the summary table - as per instructor feedback, let's forget about those for now and work on tidying the raw data.


* The raw data (list elements 3 through 6) contains 1) pre and post test scores for each lesson and each classroom condition and 2) the total time spent off task for each of the classroom conditions/lessons, divided based on the type of off task behvior (self-distraction, peer distraction etc.).

* Because the list of options for time off task is so cumbersome, let's create two tidy data frames, one for test scores and one for total time off task. We'll first work on the test scores.

First, tidy each separately. Use leave condition as the "lesson" column. No need to parse the string.
```{r echo=TRUE, eval=TRUE}
pre_df <- 
  janitor::clean_names(data_tables$`Pre-Test Scores by Lesson`) %>%
  select(-number, -x_1) %>%
  gather(condition, score, pre_test_plate_tectonics_sparse_classroom:total_pre_test_scores_decorated_classroom) %>%
  mutate(pre.post = ifelse(stringr::str_detect(condition, 'pre'), "pre", "post")) %>%
  mutate(sparse.decorated = ifelse(stringr::str_detect(condition, 'sparse'), "sparse", ifelse(stringr::str_detect(condition, 'decorated'), "decorated", NA)))
head(pre_df)
```

```{r echo=TRUE, eval=TRUE}
post_df <- 
  janitor::clean_names(data_tables$`Post-Test Scores by Lesson`) %>%
  select(-number, -x_1) %>%
  gather(condition, score, post_test_plate_tectonics_sparse_classroom:total_post_test_scores_decorated_classroom) %>%
  mutate(pre.post = ifelse(stringr::str_detect(condition, 'pre'), "pre", "post")) %>%
  mutate(sparse.decorated = ifelse(stringr::str_detect(condition, 'sparse'), "sparse", ifelse(stringr::str_detect(condition, 'decorated'), "decorated", NA)))
head(post_df)
```

Now, concatenate the pre and post test results
```{r echo=TRUE, eval=TRUE}
test_scores_df <- 
  rbind(pre_df, post_df)
head(test_scores_df)
```

Finally, let's again replace "absent" entries with NA

```{r echo=TRUe, eval=TRUE}
test_scores_df[test_scores_df=="Absent"] = NA
test_scores_df[test_scores_df=="absent"] = NA
```

Remove the participant (15) who was excluded from analyses due to absences
```{r echo=TRUE, eval=TRUE}
test_scores_df <- test_scores_df %>%
  filter(stringr::str_detect(id, "cs15")==FALSE)
```

Cool, now we've got a tidy data frame for our test scores. Note, that if we wanted to perform some sort of summary only over a given lesson, we'd use string logic on the column "condition" to effectivley pull only one lesson out.

Let's save this as a csv to tidy_raw_test_scores.
```{r echo=TRUE, eval=TRUE}
readr::write_csv(test_scores_df, here::here("Data", "tidy_raw_test_scores.csv"))
```


Now, let's do the same for the time spent off task.
```{r echo=TRUe, eval=TRUE}
sparse_df <- janitor::clean_names(data_tables$`TOT by Lesson Sparse condition`) %>%
  select(-number, -x_1) %>%
  gather(condition, score, plate_tec_self:sparse_total_time_off_task) %>%
  mutate(sparse.decorated = "sparse") %>%
  mutate(category = ifelse(stringr::str_detect(condition, 'self'), 'self', ifelse(stringr::str_detect(condition, 'peer'), 'peer', ifelse(stringr::str_detect(condition, 'environment'), 'envr', ifelse(stringr::str_detect(condition, 'other'), 'other', 'tot')))))

decorated_df <- janitor::clean_names(data_tables$`TOT by Lesson Decorated cond.`) %>%
  select(-number, -x_1) %>%
  gather(condition, score, stone_tools_self:decorated_total_time_off_task) %>%
  mutate(sparse.decorated = "decorated") %>%
   mutate(category = ifelse(stringr::str_detect(condition, 'self'), 'self', ifelse(stringr::str_detect(condition, 'peer'), 'peer', ifelse(stringr::str_detect(condition, 'environment'), 'envr', ifelse(stringr::str_detect(condition, 'other'), 'other', 'tot')))))

time_off_task_df <- rbind(sparse_df, decorated_df)

time_off_task_df[time_off_task_df=="Absent"] <- NA
time_off_task_df[time_off_task_df=="absent"] <- NA
time_off_task_df[time_off_task_df=="Abent"] <- NA

# remove participant 15 who was absent and excluded from analyses
time_off_task_df <- time_off_task_df %>%
  filter(stringr::str_detect(id, "cs15")==FALSE)

head(time_off_task_df)

readr::write_csv(time_off_task_df, here::here("Data", "tidy_raw_time_off_task.csv"))
```


* alright, now that we've tidied the data, let's (re)load the tidy dataframe and perform our EDA

### Exploratory Data Analysis

First, load the data

```{r echo=TRUE, eval=TRUE}
test_scores <- dplyr::as_tibble(read.csv(here::here("Data", "tidy_raw_test_scores.csv")))
off_task <- dplyr::as_tibble(read.csv(here::here("Data", "tidy_raw_time_off_task.csv")))
```

###### 1) Issues encountered with the data
There weren't really any big issues. Some entries were listed as absent. During our data tidying, we converted these to NA to help us handle these cases smoothly with R. Also, the column names (now condition variable) are a little messy. It took a little work to parse them in order to make them more neat and construct atidy data frame. In particular, it's really a pain to parse them in order to get the lesson title out. This shouldn't be too much of an issue, however. We can use string matching from the pacakage `stringr` on the column "condition" if we wish to pull out data for one particular lesson.

###### 2) Descriptive statistics from the paper

* the first descriptive statistic reported is the mean age of the children (5.37 years) as well as the number of male (12) and female (12) students. The raw data provided does not allow us to reproduce these summaries. In addition, we cannot reproduce the summaries of the student's demographic (race/ethnicity) information. However, we can confirm that the total number of participants was 24.

```{r echo=TRUE, eval=TRUE}
# there are 24 disitninct study participants
length(unique(off_task$id))
```
We only get 23 here because we have already removed the student who was exlcluded from analyses due to absences in the tidying step.

* The next notable summary statistic reported is the mean pre-test score. This is reported to be 22.7%. We can confirm this.

```{r echo=TRUE, eval=TRUE}
test_scores %>%
  filter((pre.post=="pre") & (stringr::str_detect(condition, "tot")==FALSE)) %>%
  summarize(mean_pre_test_score = 100*mean(score))
```

* For many of the anlayses in the paper, the authors present descriptive visualizations/summaries, then they quantify the differences they observe with statistical tests. We'll leave the quanitifcation for later (P4), but walk through the descriptive visualizations here.

* First, we'll repoduce the stats/figures for time off task as a function of classroom condition graph

The authors state that overall, children were on task 66.5% percent of the time. Let's confirm this without using the reported totals by the authors.

```{r echo=TRUE, eval=TRUE}
mean_tof <- 
  off_task %>%
  na.omit() %>%
  group_by(sparse.decorated, category) %>%
  select(score) %>%
  mutate(score = as.numeric(as.character(score))) %>%
  summarize(means = mean(score), se = sd(score)/sqrt(length(score))) %>%
  filter(category!="tot")

# time ON-task across both conditions
1 - 0.5 * (sum(filter(mean_tof, sparse.decorated=='decorated')$means) + sum(filter(mean_tof, sparse.decorated=='sparse')$means))
```
As reported, students are ON task for about 66.4 percent of the time. we're not sure why this isn't coming out to exactly 66.5 as reported. Further, we see that the time off task is quite different for the two groups:

```{r echo=TRUE, eval=TRUE}
# time of task decorated
sum(filter(mean_tof, sparse.decorated=='decorated')$means)

# time of task sparse
sum(filter(mean_tof, sparse.decorated=='sparse')$means)
```
Again, these summaries stats don't exactly match those reported in the paper(38.58 and 28.42, respectively). Not sure why this is happening.

Finally, we can reporduce the summary plot for this:
```{r echo=TRUE, eval=TRUE}
ggplot(mean_tof, aes(x=category, y=means)) + geom_bar(stat="identity") + facet_grid(~sparse.decorated) + 
  geom_errorbar(aes(ymin=means-se, ymax=means+se),
                size=.3,
                width=.2)
```
